---
title: "Exercise: Bar plots in ggplot"
output: learnr::tutorial
runtime: shiny_prerendered
description: >
  Exercises related to creating bar plots in ggplot.
---

```{r setup, include=FALSE}
library(learnr)
library(testwhat)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.timelimit = 60, exercise.checker=testwhat::testwhat_learnr)

require(tidyverse)
data(mtcars)
penguins<- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-28/penguins.csv")
```

We are going to use the penguins data to produce a variety of bar plots using `ggplot`. These are the same plots that you created in the previous set of exercises, but it is goo

```{r}
head(penguins)

```
### Exercise 1

Produce a bar plot to work out which species of penguin is most common:

```{r barplot1, exercise=TRUE}



```

```{r barplot1-solution}

ggplot(penguins) + 
  geom_bar(aes(species))

```


```{r barplot1-check}

ex() %>% {
  check_error(.)
  check_function(., "ggplot") %>% check_arg(., "data", arg_not_specified_msg = "Did you specify the data (either through the pipe or in ggplot)?")
  check_function(., "geom_bar") %>% check_arg(., "mapping", arg_not_specified_msg = "You need to specify your aesthetics using aes()") %>% check_equal(.)
  check_function(., "aes") 
}

```

### Exercise 2

Produce a bar plot that will compare the distribution of species within each island: 

```{r barplot2, exercise=TRUE}


```

```{r barplot2-solution}


ggplot(penguins) +
  geom_bar(aes(island, fill=species), position=position_dodge())

# Not particularly satisfying...you can force all levels to appear by adding a row of data for each missing bar:

penguins %>% 
  # Manually add data in 
  bind_rows(data.frame(species=c("Chinstrap","Gentoo","Chinstrap","Gentoo"), island=c("Biscoe","Dream","Torgersen","Torgersen"))) %>% 
  ggplot() +
  geom_bar(aes(island, fill=species), position=position_dodge())

```

```{r barplot2-check}
ex() %>% {
  check_error(.)
  check_function(., "ggplot") %>% check_arg(., "data", arg_not_specified_msg = "Did you specify the data (either through the pipe or in ggplot)?")
  check_function(., "geom_bar") %>% {
    check_arg(., "mapping", arg_not_specified_msg = "You need to specify your aesthetics using aes()") %>% check_equal(.)
    check_arg(., "position", arg_not_specified_msg = "Specify position=position_dodge() to put the bars beside each other")
  }
  check_function(., "aes") 
}
success_msg("Great Work! Check out the solutions for a tip to get all of the bars even :)")
```

### Exercise 3

Calculate the maximum bill length for each species of penguin and plot these on a bar plot (Tip: You may need to exclude missing values)

*When finding the maximum call the column bill_length otherwise you may get told you are wrong when you aren't*

```{r barplot3, exercise=TRUE}


```

```{r barplot3-solution}

penguins %>% 
  group_by(species) %>% 
  summarise(bill_length=max(bill_length_mm, na.rm=TRUE)) %>% 
  ggplot() +
  geom_col(aes(species, bill_length))


```

```{r barplot3-check}
ex() %>% {
  check_error(.)
  check_function(., "summarise", not_called_msg="You need to find the maximum bill length for each species") %>% check_result(.) %>% check_equal(.)
  check_function(., "ggplot") %>% check_arg(., "data", arg_not_specified_msg = "Did you specify the data (either through the pipe or in ggplot)?")
  check_function(., "geom_col", not_called_msg="geom_col() is the easiest way to plot this information") %>% check_arg(., "mapping", arg_not_specified_msg = "You need to specify your aesthetics using aes()") %>% check_equal(.)
  check_function(., "aes")
}
```
