---
title: "Exercise: Box plots in Base R"
output: learnr::tutorial
runtime: shiny_prerendered
description: >
  Exercises related to creating box plots in Base R.
---

```{r setup, include=FALSE}
library(learnr)
library(testwhat)
knitr::opts_chunk$set(echo = FALSE, message=FALSE)
tutorial_options(exercise.timelimit = 60, exercise.checker=testwhat::testwhat_learnr)

require(tidyverse)
penguins<- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-28/penguins.csv")
```

```{r penguins_setup, message=FALSE}

penguins<- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-28/penguins.csv")

```

We are going to use the penguins data to produce a variety of box plots using ggplot.

```{r}
head(penguins)

```

### Exercise 1

Produce a box plot showing body mass:

```{r barplot1, exercise=TRUE, exercise.setup="penguins_setup", message=FALSE}



```

```{r barplot1-solution}

boxplot(penguins$body_mass_g)

```


```{r barplot1-check}

ex() %>% {
  check_error(.)
  check_function(., "boxplot") %>% check_arg(., "x") %>% check_equal(.)
}

```

### Exercise 2

Produce a box plot that will compare the distribution of body weight by year: 

```{r barplot2, exercise=TRUE, exercise.setup="penguins_setup"}


```

```{r barplot2-solution}

boxplot(body_mass_g~year, data=penguins)

```

```{r barplot2-check}

ex() %>% {
  check_error(.)
  check_function(., "boxplot") %>% {
    check_arg(., "formula", arg_not_specified_msg = "The easiest way to do this is to specify a formula") %>% check_equal(.)
    check_arg(., "data", arg_not_specified_msg="Specifying the data argument when using a formula will make your code more readable") 
  }
}

```

### Exercise 3

Produce a boxplot that will describe the distribution of body mass for each species within each year. The observations within a species should appear next to one another.

```{r barplot3, exercise=TRUE, exercise.setup="penguins_setup"}


```

```{r barplot3-solution}

boxplot(body_mass_g~year+species, data=penguins)


```

```{r barplot3-check}

ex() %>% {
  check_error(.)
  check_function(., "boxplot") %>% {
    check_arg(., "formula", arg_not_specified_msg = "The easiest way to do this is to specify a formula") %>% check_equal(., eval=FALSE, eq_fun=function(x, y){str_replace_all(x, "[[:blank:]]", "")==str_replace_all(y, "[[:blank:]]", "")})
    check_arg(., "data", arg_not_specified_msg="Specifying the data argument when using a formula will make your code more readable") 
  }
}

```
