---
title: "Exercise: Box plots in ggplot"
output: learnr::tutorial
runtime: shiny_prerendered
description: >
  Exercises related to creating box plots in ggplot.
---

```{r setup, include=FALSE}
library(learnr)
library(testwhat)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.timelimit = 60, exercise.checker=testwhat::testwhat_learnr)

require(tidyverse)
data(mtcars)
penguins<- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-28/penguins.csv")
penguins %>% mutate(year=as.factor(year)) -> penguins
```

We are going to use the penguins data to produce a variety of box plots using ggplot.

```{r}
head(penguins)

```

### Exercise 1

Produce a box plot showing body mass:

```{r barplot1, exercise=TRUE}



```

```{r barplot1-solution}
ggplot(penguins) +
  geom_boxplot(aes(body_mass_g))
```


```{r barplot1-check}

ex() %>% {
  check_error(.)
  check_function(., "geom_boxplot") %>% check_arg(., "mapping") %>% check_equal(.)
}
```

### Exercise 2

Produce a box plot that will compare the distribution of body weight by year (you should not separate the groups using colour): 

```{r barplot2, exercise=TRUE}


```

```{r barplot2-solution}
penguins %>%
  ggplot() + 
  geom_boxplot(aes(x=year, y=body_mass_g))

```

```{r barplot2-check}
ex() %>% {
  check_error(.)
  check_function(., "geom_boxplot") %>% check_arg(., "mapping") %>% check_equal(.)
}
```

### Exercise 3

Produce a boxplot that will describe the distribution of body mass for each species within each year. The observations within a species should appear next to one another.

```{r barplot3, exercise=TRUE}


```

```{r barplot3-solution}

penguins %>%
  ggplot() + 
  geom_boxplot(aes(x=species, y=body_mass_g, fill=year))


```

```{r barplot3-check}
ex() %>% {
  check_error(.)
  check_function(., "geom_boxplot") %>% check_arg(., "mapping") %>% check_equal(.)
}
```
