---
title: "Exercise: pivot_wider"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(testwhat)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.timelimit = 60, exercise.checker=testwhat::testwhat_learnr)

require(tidyverse)
penguins<- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-28/penguins.csv")
penguins <- penguins %>%  mutate(Sample_Number=1:nrow(penguins)) %>% pivot_longer(bill_length_mm:body_mass_g, names_to="Measurement", values_to="Observations")
test <- tibble(Name=rep(c("Kim","Louise","Susan","Johnny","Scott","Stephen","David","Catriona","Rebecca","Donna","Lynne","John","Billy"), each=5), Assessment=rep(1:5, times=13), Grade=c(sample(70:90, 5, replace = TRUE),sample(60:80, 5, replace = TRUE), sample(75:85, 5, replace = TRUE), sample(50:60, 5, replace = TRUE),sample(40:60, 5, replace = TRUE), sample(80:100, 5, replace = TRUE), sample(60:70, 5, replace = TRUE), sample(35:50, 5, replace = TRUE), sample(45:70, 5, replace = TRUE), sample(80:100, 5, replace = TRUE), sample(48:62, 5, replace = TRUE), sample(55:75, 5, replace = TRUE), sample(60:70, 5, replace = TRUE)))

```


### Exercise 1

The data set `penguins` has been transformed into the following format:

```{r peguins_print, echo=FALSE}
penguins
```

In the box below, use the `pivot_wider()` function to get the pre-loaded penguins data into tidy data format, where each measurement is in its own column. 

```{r pivot_wider1, exercise=TRUE}
# tidy the penguins data


```

```{r pivot_wider1-solution}
# tidy the penguins data
penguins %>% pivot_wider(names_from=Measurement, values_from=Observations)

```


```{r pivot_wider1-check}

ex() %>% {
  check_error(.)
  check_function(., "pivot_wider", index=1) %>% {
    check_arg(., "names_from") %>% check_equal(., eval=FALSE)
    check_arg(., "values_from") %>% check_equal(., eval=FALSE)
  }
}
```

### Exercise 2

A data set containing student grades across five different assessments has been loaded into an R session. The data is stored in a data frame called `test` and is shown below:

```{r print_grades, echo=FALSE}

test

```

In the box below, get the data into tidy format, where each assessment forms a column. Make sure to name the columns appropriately by adding "Assessment" to the assessment numbers:

```{r pivot_wider2, exercise=TRUE}

# tidy the test data set

```

```{r pivot_wider2-solution}

test %>% pivot_wider(names_from=Assessment, values_from=Grade, names_prefix="Assessment")

```

```{r pivot_wider2-check}
ex() %>%{
  check_error(.)
  check_function(., "pivot_wider") %>% {
    check_arg(., "names_from") %>% check_equal(., eval=FALSE, eq_fun=function(x,y) {stringr::str_extract(x, "[[:alpha:]]+" )==stringr::str_extract(y, "[[:alpha:]]+" )})
    check_arg(., "values_from") %>% check_equal(., eval=FALSE, eq_fun=function(x,y) {stringr::str_extract(x, "[[:alpha:]]+" )==stringr::str_extract(y, "[[:alpha:]]+" )})
    check_arg(., "names_prefix") %>% check_equal(., eq_fun=function(x, y){tolower(x)==tolower(y)})
  }
}
```

