---
title: "Exercise: Subsetting Data"
output: learnr::tutorial
runtime: shiny_prerendered
description: >
  Set of exercises relating to Activity 4.4 (Subsetting Data).
---

```{r setup, include=FALSE}
library(learnr)
library(testwhat)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.timelimit = 60, exercise.checker=testwhat::testwhat_learnr)

require(tidyverse)
data(mtcars)
```

For the following examples you should use functions from `dplyr` to extract the relevant pieces of data from the `mtcars` data set:

```{r show_data}

head(mtcars)

```

### Exercise 1

Find the cars which get at least 20 miles per gallon (`mpg`).

```{r filter1, exercise=TRUE}


```

```{r filter1-solution}
# tidy the penguins data
mtcars %>% filter(mpg>=20) %>% arrange(mpg)

```


```{r filter1-check}

ex() %>% {
  check_error(.)
  check_function(., "filter", index=1) %>% check_result(.) %>% check_equal(.)
}
```

### Exercise 2

Order the data in `mtcars` by highest to lowest weight (`wt`) 

```{r filter2, exercise=TRUE}


```

```{r filter2-solution}

mtcars %>% arrange(desc(wt))

```

```{r filter2-check}
ex() %>%{
  check_error(.)
  check_function(., "arrange") %>% check_result(.) %>% check_equal(., incorrect_msg="Did you sort the data in decreasing order?")
}
```


### Exercise 3

Extract the rows from the `mtcars` data set where the number of gears (`gear`) is not equal to 4. Order the results by increasing horsepower (`hp`)

```{r filter3, exercise=TRUE}


```

```{r filter3-solution}

mtcars %>% filter(gear!=4) %>% arrange(hp)

```

```{r filter3-check}
ex() %>%{
  check_error(.)
  check_or(.,
           {check_function(.,"filter") %>% check_result(.) %>% check_equal(.)
             check_function(.,"arrange") %>% check_result(.) %>% check_equal(.)},
           override_solution_code(., "mtcars %>% arrange(hp) %>% filter(gear!=4)") %>% {check_function(.,"arrange") %>% check_result(.) %>% check_equal(.)
             check_function(.,"filter") %>% check_result(.) %>% check_equal(.)})
}
```
