---
title: "Exercise: Combining Multiple Data Sets"
output: learnr::tutorial
runtime: shiny_prerendered
description: >
  Set of exercises relating to Activity 4.3 (Combining Multiple Data Sets).
---

```{r setup, include=FALSE}
library(learnr)
library(testwhat)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.timelimit = 60, exercise.checker=testwhat::testwhat_learnr)

require(tidyverse)
colour <- tibble(Name=c("Sophie","Lauren","Greg","Callum","Ainsley","Alistair"), colour=sample(c("Pink","Blue","Red","Green","Purple","Yellow")))

pet <- tibble(Name=c("Stacey","Lauren","Ainsley","Graham","Chris","Greg"), Pet=c("Dog","Cat","Dog","Fish","Hamster","Cat"))
```

I have two data sets, `colour` and `pet`, which are shown below:

```{r exercise1_setup}

knitr::kable(colour)

knitr::kable(pet)


```


### Exercise 1

I want to keep all rows in both data sets while merging rows which have a match.

```{r Question1, echo=FALSE}

question("What type of join could you use here?",
  answer("left"),
  answer("right"),
  answer("full", correct=TRUE),
  answer("inner"),
  answer("anti"),
  answer("semi")
)

```

What would the code be to do this in R?



```{r exercise1, exercise=TRUE}

```


```{r exercise1-solution}

colour %>% full_join(pet)

```

```{r exercise1-check}

# this is really unsatisfying - come back to this at some point
ex() %>% check_function("full_join") %>% check_result()


```

### Exercise 2

I want to merge the two data sets but only keep the rows in both data sets which have a match.

```{r Question2, echo=FALSE}

question("What type of join could you use here?",
  answer("left"),
  answer("right"),
  answer("full"),
  answer("inner", correct=TRUE),
  answer("anti"),
  answer("semi")
)

```

What would the code be to do this in R?

```{r exercise2, exercise=TRUE}

```

```{r exercise2-solution}

colour %>% inner_join(pet)

```

```{r exercise2-check}

# this is really unsatisfying - come back to this at some point
ex() %>% check_function("inner_join") %>% check_result()


```

### Exercise 3

I want to keep all the rows in the pets data set that have a match in the colour data set - I do not want to merge the data sets.

```{r Question3, echo=FALSE}

question("What type of join could you use here?",
  answer("left"),
  answer("right"),
  answer("full"),
  answer("inner"),
  answer("anti"),
  answer("semi", correct=TRUE)
)

```

What would the code be to do this in R?

```{r exercise3, exercise=TRUE}

```

```{r exercise3-solution}

pet %>% semi_join(colour)

```

```{r exercise3-check}

# this is really unsatisfying - come back to this at some point
ex() %>% check_function("semi_join") %>% check_result()


```

### Exercise 4

I want to keep all the rows in the colour data set that have a match in the pet data set - I do not want to merge the data sets.

```{r Question4, echo=FALSE}

question("What type of join could you use here?",
  answer("left"),
  answer("right"),
  answer("full"),
  answer("inner"),
  answer("anti", correct=TRUE),
  answer("semi")
)

```

What would the code be to do this in R?

```{r exercise4, exercise=TRUE}

```


```{r exercise4-solution}

colour %>% anti_join(pet)

```

```{r exercise4-check}

# this is really unsatisfying - come back to this at some point
ex() %>% check_function("anti_join") %>% check_result()


```
