---
title: "Exercise: Transforming Data"
output: learnr::tutorial
runtime: shiny_prerendered
description: >
  First set of exercises relating to Activity 4.6 (Transforming Data).
---

```{r setup, include=FALSE}
library(learnr)
library(testwhat)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.timelimit = 60, exercise.checker=testwhat::testwhat_learnr)

require(tidyverse)
data(mtcars)
penguins<- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-28/penguins.csv")
```

For the following examples you should use functions from `dplyr` to carry out the relevant transformations on the `mtcars` data set:

```{r show_data}

head(mtcars)

```

### Exercise 1

The horse-power data in the `mtcars` data set are skewed:

```{r}
hist(mtcars$hp)
```

Add a new column to the data set, which contains the square root of `hp`

```{r filter1, exercise=TRUE}



```

```{r filter1-solution}
# tidy the penguins data
mtcars %>% mutate(sqrt_hp=sqrt(hp))

```


```{r filter1-check}

ex() %>% {
  check_error(.)
  check_function(., "mutate") %>% check_result(.) %>% check_equal(.)
}
```

### Exercise 2

Standardise the `mpg` column using the standard deviation. Distinguish between automatic and manual transmissions (`am`) 

```{r filter2, exercise=TRUE}


```

```{r filter2-solution}

mtcars %>% group_by(am) %>% mutate(mpg_std = mpg/sd(mpg))

```

```{r filter2-check}
ex() %>%{
  check_error(.)
  check_function(., "group_by") 
  check_function(., "mutate")%>% check_result(.) %>% check_equal(., incorrect_msg="Did you group by transmission type before using mutate? Try checking your calculation - you should divide mpg by its standard deviation.")
}
```

### Exercise 3

Using the penguins data:

```{r}
penguins
```

calculate the log bill length and bill depth by species.

```{r filter3, exercise=TRUE}


```

```{r filter3-solution}

penguins %>% mutate(across(starts_with("bill_"), log))

```

```{r filter3-check}
ex() %>%{
  check_error(.) 
  check_function(., "mutate")%>% check_result(.) %>% check_equal(., incorrect_msg="Did you take the log of the bill related columns correctly?")
}
```
